\documentclass[a4paper,cleardoubleempty,BCOR1cm]{scrbook}
\input{header}

\title{Bachelorarbeit}
\author{Peter Trost \thanks{e-mail: peter.trost@student.uni-tuebingen.de}}
\date{\today}
\begin{document}

\input{teaser}

\chapter*{Abstract}
Due to advances in deep learning and progress in high-performance computing, self driving cars gain increasing popularity. Currently, Deep Neural Networks perform well on tasks such as semantic segmentation and object recognition. These are relevant tasks for the car as it needs to make decisions depending on its environment. Deep Neural Networks need large amounts of data to learn how to properly classify or recognize objects in the driving environment so the system can make the right decisions. Currently, the best results in training are achieved via supervised training, i.e. having the expected output (ground truth) for each given input. Creating datasets for autonomous driving applications that contain real world images and accurate ground truth is time intensive and therefore very costly. In contrast there are many approaches that can cheaply generate loads of synthetic images from virtual worlds with accurate pixel-level labeling. Models trained on synthetically generated datasets however do not perform well in the real world due to the domain shift (changes in texture, lighting, etc.). The research area of Domain Adaptation tries to adapt these two domains so that the difference between them is reduced in order to make it possible to train Deep Neural Networks on cheap synthetic images and still able to perform well in the real world. There are many different approaches for Domain Adaptation. Because it generates realistic looking images Generative Adversarial Networks \cite{NIPS2014_5423} has recently gained attention by the research community. This work shows three alterations of this network architecture, namely CycleGAN \cite{DBLP:journals/corr/ZhuPIE17}, CyCADA \cite{DBLP:journals/corr/abs-1711-03213} and SG-GAN \cite{DBLP:journals/corr/abs-1801-01726} and compares them on the synthetic-to-real domain shift using GTA5 \cite{Richter_2016_ECCV} and Cityscapes datasets \cite{Cordts_2016_CVPR}. Models of the named techniques pre-trained on the translation from GTA5 to Cityscapes data were used to translate a sampleset of images. Semantic segmentation is then performed on these translated samples. To evaluate the techniques' performances the results of the semantic segmentation is compared to the ground truth of the corresponding images.


\chapter*{Acknowledgments}
I want to thank everyone that helped me create this work. Especially Anastasia Bitter for her emotional and active support, Stephan Richter for explaining some aspects of the GTA dataset to me and Taesung Park for sending me a pretrained CycleGAN model. Further I want to thank my mentors Despoina Paschalidou and Yiyi Liao for their guidance and support and Professor Andreas Geiger for enabling me to work on this topic and the help in defining it precisely.

\tableofcontents

%% braucht kein Mensch ...
%\listoffigures
%\listoftables


\input{content/intro}
\input{content/foundations}
\input{content/related_work}
\input{content/techniques}
\input{content/experiments}
\input{content/conclusion}


\appendix
\chapter{Appendix}

\bibliographystyle{alpha}
\bibliography{bibliography}

\end{document}

